Country-Level Impact of Education on Entrepreneurship

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Minor editing

#### Research Question

@@

#### Estimation Strategy

##### Causal Chain

@@

##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship

@@

##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System

@@

##### Control Variables: Controlling for Classic Determinants of Entrepreneurship

@@

##### Regressions

>>>>

### Research Question

@@

### Estimation Strategy

#### Causal Chain

@@

#### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship

@@

#### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System

@@

#### Control Variables: Controlling for Classic Determinants of Entrepreneurship

@@

#### Regressions
